Enter our title here

### 2017-09-27 manuscript.tex
added textbox and captioning for code

%-----------------------------------------------------------------------------------------------------
%Substitute this all with tise_style
\documentclass[12pt]{article}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text
\usepackage{url}
\usepackage{graphicx}
% Sets margins to 1 in
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{1.3in}%
%\addtolength{\topmargin}{-.8in}%
%-----------------------------------------------------------------------------------------------------

@@

@@

3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code
It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.

@@

\begin{verbatim}
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
## Quick check 2

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```

\end{verbatim}

@@

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{ECA_jasa}
\bibliography{library}
% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(

>>>>

%-----------------------------------------------------------------------------------------------------
%Substitute this all with tise_style
\documentclass[12pt]{article}
\usepackage{natbib}  % used for citations
\usepackage[parfill]{parskip} %used for formatting style of text
\usepackage{url}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{fancyvrb}
% Sets margins to 1 in
%\addtolength{\oddsidemargin}{-.5in}%
%\addtolength{\evensidemargin}{-.5in}%
%\addtolength{\textwidth}{1in}%
%\addtolength{\textheight}{1.3in}%
%\addtolength{\topmargin}{-.8in}%
%-----------------------------------------------------------------------------------------------------

@@

\doublespacing

@@

3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.

@@

\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
## Quick check 2

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{Verbatim}
\end{figure}

@@

%Use this for final submission
%\bibliographystyle{ECA_jasa}
\bibliographystyle{plainnat}
\bibliography{library}
% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(
